Mean and sd of null distribution

### 2020-09-03 manual_distribution_max.Rmd
bootstrap code added

@@

```{r shape_rate}

```{r norm_max}

@@

>>>>

# Question:1

I'm definite that the theeretical distribution of Jensen Shannon statistic follows a Chi-squared distribution with $m$ degrees of freedom. If $m$ is sufficiently large, Chi square distribution will tend to a Normal distribution with mean $m$ and variance $2m$.

Empirical test: In my case, do we mean that no matter what is the underlying distribution of the dataset, if you compute Jensen Shannon distances they will be normal like?

Let's find out!

Simulation study:

 1. Fix $n$.
 2. Take a particular distribution and generate $N$ random samples of size $n$ each.
 3. Compute pairwise distances for each random sample.
 4. Construct a histogram to see of the pairwise distances follow Normal?

# Question:2

Let's suppose they are normal! How would the max of these normal distances behave? Would the distribution of the maximum differ if you are taking max between 2 random variables or maximum between 10 random variables?

Yes they would! So what do you do about it?

We want to make the distribution of the max same for any $n$. By making the distribution same, we just mean that at least the mean and sd of the distribution of the maximum should be same for varied n. This means we should be able to compare values across different $n$. What is a consistent estimator of max?

## Simulation Study

Aim:  To see if norm_max is working after a certain $n$ for all cases.
 1. Generate N(1:10,10) distribution and compute distribution of max and norm_max.  
 2. Generate N(10,1:10) distribution and compute distribution of max and norm_max.

## Behavior of mean and sd of the distribution of maximum

@@

```{r norm_max_new}

@@

Aim:  To compute mean and sd by bootstrap method for small samples and compute norm_max to see if it is working for $n$ cases.

## Non-parametric bootstrap

Assuming a data set $x = (x_1, ..., x_n)$ is available.  
1. Fix the number of bootstrap re-samples $N$. Often $N \in [1000, 2000]$.  
2. Sample a new data set $x^{*}$ set of size $n$ from $x$ with replacement (this is equivalent to sampling from the empirical cdf $\hat{F}$).  
3. Estimate $\theta$ from $x^*$. Call the estimate $\hat{\theta}$ $\forall i \in {1,\ldots, N}$. Store.  
4. Repeat step 2 and 3 $N$ times.  
5. Consider the empirical distribution of ($\hat{\theta}^*_1, \hat{\theta}^*_2, \ldots, \hat{\theta}^*_N$) as an approximation of the true
distribution of $\hat{\theta}$.

We assume that distances are normal, but we do not assume anything about the distribution of max distances. So using the non-paramteric bootstrap approach to estimate the $\theta = (\mu, \sigma)$.

I construct the data structure for $n = 2$ here to ensure that the methodology is correct.

| N 	| $x_1$    	| $x_2$    	| max 	|
|---	|-------	|-------	|------	|----	|
| 1 	| $x_{1,1}$  	| $x_{1,2}$  	| $m_1$   	|
| 2 	| .     	| .     	| $m_2$   	|
| . 	| .     	| .     	| .    	|
| . 	| .     	| .     	| .    	|
| N 	| $x_{1, N}$ 	| $x_{2, N}$ 	| $m_N$   	|

Question:3

This is just for one level! What do you do for the other level?

Do you take median or max. Given that you take median how do you normalise for the value of $n$ there? What is a consistent estimator of median?
